Sample Title:\\with Forced Linebreak

### 2022-10-20 publication/publication.tex
#37: Picture insert und word count

%% Include graphic for one column with specific place 
\newcommand{\includegraphicsOneCol}[3]{
	\begin{figure}[h]
		\includegraphics[width=\linewidth]{#1}
		\caption{#2}
  	\end{figure}
	\label{#3}
  	\increasecounter{fig}{1}
}

@@

%\title[Convergence of shearingrate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize]{
%	Convergence of shearingrate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize
%}

@@

@@

@@

% BIBLOGRAPHY ==============================================================================================================

>>>>

%% Include graphic for one column with specific place 
\newcommand{\includegraphicsOneCol}[3]{
	\begin{figure}[h]
		\includegraphics[width=0.9\linewidth]{#1}
		\caption{#2}
  	\end{figure}
	\label{#3}
  	\increasecounter{fig}{1}
}

@@

%\title[Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize]{
%	Convergence of shearing rate $\omega_{\mathrm{E}\times\mathrm{B}}$ with boxsize
%}

@@

\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.3_boxsize1x1_Ns16_Nvpar64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

\includegraphicsOneCol{S6_rlt6.0/boxsize3x1/Ns16/Nvpar48/Nmu9/S6_rlt6.0_boxsize3x1_Ns16_Nvpar48_Nmu9_wexb_selection.pdf}{Test}{fig:eflux}

\includegraphicsOneCol{Comparison/Gradient-Length/S6_rlt6.0-6.2_boxsize2x2_Ns16_Nvpar48-64_Nmu9_eflux_comparison.pdf}{Test}{fig:eflux}

@@

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_wexb_comparison.pdf}{Test}{fig:test}

%\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_eflux_comparison.pdf}{Test}{fig:test}

\includegraphicsTwoCol{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1_Ns16_Nvpar48_Nmu9_comparison.pdf}{Test}{fig:test}

\increasecounter{fig}{2}

@@

% BIBLIOGRAPHY ==============================================================================================================
